Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-03-21 article.tex
Remove mention of SBML export which is not yet implemented

Several commonly used reactions are predefined as \texttt{MassAction}
subclasses, such as \texttt{MichaelisMenten}
(\(S + E \leftrightarrow ES \rightarrow P + E\)) and its approximate
form without the intermediate species \(ES\), and it is also simple to
implement your own as subclasses of \texttt{RateLaw} or
\texttt{MassAction}. Additionally, SimBio supports importing from and
exporting to \ac{SBML}, and downloading them directly from BioModels
\cite{malik-sheriffBioModels15Years2020} (Figure~\ref{fig-simbio-io}).

>>>>

Several commonly used reactions are predefined as \texttt{MassAction} subclasses,
such as \texttt{MichaelisMenten} (\(S + E \leftrightarrow ES \rightarrow P + E\))
and its approximate form without the intermediate species \(ES\),
and it is also simple to implement used-defined ones
as subclasses of \texttt{RateLaw} or \texttt{MassAction}.
Additionally, SimBio supports importing models from \ac{SBML},
and downloading them directly from BioModels \cite{malik-sheriffBioModels15Years2020} (Figure~\ref{fig-simbio-io}).
